---
title: "Capex_comput "
output: html_notebook
---
# Capex data processing for base year calibration - IMACLIM-R electricity nexus

## Sources 
Baseyear CAPEX are given by IRENA (2020) Renewable Power Generation Costs in 2019 when
data is available or raisonable assumption is possible.
Installed capacity from IRENA (2020)

## Methodology description
- when data is available for baseyear (2014) or reasonnable assumption was possible (e.g. Europe as a mean of European Countries), 2014 IRENA (2020) data is used (Step 1)
- when IRENA (2020a) only provides 2019 data, the learning curve is used to extrapolate 2014 investment costs based on addition of installed capacity between 2014 and 2019 (Step 2)
- when IRENA (2020a) regional coverage is unsuitable for analysis or that the learning curve process does not yield sound results (in our case, CSP and WNO), an alternative method is used. The world mean cost decrease between 2019 and 2014 is applied to regional cost data from IRENA (2020b) (Step 2bis).


```{=latex}
$CINV_Q = CINV_Qref*(Q/Qref)^(-b) and b = - ln(1-PR)/ln(2) with PR = Progress Ratio$
```

```{r, results = "hide"}
library(tidyverse)
```
Data import: installed capacity in 2014 and 2019 per IMACLIM-R region and solar & wind technology.

```{r, results = "hide"}
anneeQ <- 2019
anneeQref <- 2014

path_data_IRENA <- "installed_cap/"

path_Q <- paste0(path_data_IRENA,"Cap_",anneeQ,"_ag.csv")
path_Qref <- paste0(path_data_IRENA,"Cap_",anneeQref,"_ag.csv")

data_Q <- read.csv(path_Q, sep = ";", header = TRUE)
names(data_Q)[3] <- "Q"
data_Qref <- read.csv(path_Qref, sep = ";", header = TRUE)
names(data_Qref)[3] <- "Qref"
```

Importing IMACLIM-R region and technology names
```{r}
#Imaclim Regions
Reg_IMC <- c("USA","Canada","Europe","OECD Pacific","CEI","China","India","Brazil",
             "Middle East","Africa","Rest of Asia","Rest of Latin America")
#Renewable energy source technologies
techno <- c("WND","WNO","CSP","CPV","RPV")

```

Hardcoding **baseyear investment costs** from IRENA (2020),Renewable Power Generation Costs in 2019

```{r}
#WND - Figure 2.5 - Hyp: EUR = mean(Germany, Sweden, Italy, UK, Spain, France), 
# CEI= EUR, Rest of Asia = CHI,Rest of Latin = mean(BRAZ, MEX). No Africa nor Middle East
costs_WND_base <- c(1904,2443,mean(2011,2146,1983,2265,1753,1795),2919,mean(2011,2146,1983,2265,1753,1795),1350,1419,2222,0,0,1350,mean(2222,2533))
#CPV - Figure 3.4 - Hyp: CAN = USA, EUR = mean(France, Germany, Italy, Spain, UK), OECD = mean(Japan, Aus), CEI = EUR, Rest of Asia = CHIN
#No Africa, Middle East, Brazil, Rest of Latin America
costs_CPV_base <- c(2885,2885,mean(2369,1600,1972,2316,1943),mean(3007,3069),mean(2369,1600,1972,2316,1943),1763,1907,0,0,0,1763,0)
#RPV (Commercial in IRENA) - Table 3.1 - Hyp : USA = mean(4 US States), CEI = EUR = mean(France, Germany, Italy, Spain), OECD Pacific = mean(Jap,Aus), #
#IND = Rest of Asia = CHI. No Brasil, Middle East, Africa, Rest of Latin America
costs_RPV_base <- c(mean(3574,3668,4004,3786),mean(3574,3668,4004,3786),mean(2880,1691,2016,3168),mean(2846,3122),mean(2880,1691,2016,3168),1661,1661,0,0,0,1661,0)
#WNO and CSP: no IRENA data
costs_WNO_base <- rep(0,length(Reg_IMC))
costs_CSP_base <- rep(0,length(Reg_IMC))
```
Hardcoding 2019 inv costs - Source: IEA (2020) "Power generation assumptions in the Stated Policies and SDS Scenarios in the World Energy Outlook 2020"

```{r}
#Hardcoding 2019 inv costs - Source: IEA (2020) "Power generation assumptions in the Stated Policies and SDS Scenarios in the World Energy Outlook 2020"
#Used for step 2, to control the learning curve process
#hyp : CAN = USA, !!!OECD PAC = JAP !!!!!, REST ASIA = CHI, REST LAT = BRAZ, CEI = RUS
costs_WND <- c(1560,1560,1560,2260,1630,1220,1060,1560,1800,1950,1220,1560)
costs_WNO <- c(4260,4260,3800,4100,4800,3000,3140,4620,4580,4440,3000,4620)
costs_CPV <- c(1220,1220,840,2070,2120,790,610,1250,1000,1600,790,1250)
costs_RPV <- c(3480,3480,1240,2030,2740,900,820,1260,1640,2200,900,1260)
#hyp supp: OECD PAC = USA, CEI = EUR
costs_CSP <- c(6500,6500,5650,6500,5650,4900,5700,5350,5250,5050,4900,5350) 
costs_CSP <- c(6500,6500,5650,6500,5650,4900,5700,5350,5250,5050,4900,5350) 
```

Manually computing the maximum country/region cost reduction between 2014 and 2019, to make sure that when applying the learning curve process (Step 2) the computed cost reduction does not exceed the maximum observed.

```{r, results = "hide"}
cost_red_max <- list()
cost_red_max["CPV"] <- 0.68 #for India, Figure 3.4
cost_red_max["RPV"] <- 0.56 #for Spain, Table 3.3
cost_red_max["WND"] <- 0.38 #for Sweden
#Not relevant for Offshore and CSP since we do not apply the same methodology as other technos
cost_red_max["WNO"] <- 1 
cost_red_max["CSP"] <- 1
```

Preparing datasets for the investment cost processing

```{r, results = "hide"}
data_CINV <- merge(data_Q,data_Qref, by = c("Technology","Region"),all.x = TRUE)
#Adding lines for Missing regions for all techno

for (i in techno){
existing_reg <- filter(data_CINV, Technology == i) %>% .$Region
for (j in which(!Reg_IMC %in% existing_reg)){
  data_CINV <- rbind(c(i,Reg_IMC[j],-1,-1),data_CINV)
}
}

#Capacity
data_CINV$Q <- as.numeric(data_CINV$Q)
data_CINV$Qref <- as.numeric(data_CINV$Qref)

#Investment costs
data_CINV$CINV_base <- rep(0,nrow(data_CINV))
data_CINV$CINV_base_IRENA<- rep(0,nrow(data_CINV))
data_CINV$CINV_2019 <- rep(0,nrow(data_CINV))

#Learning applies to cumulated installed capacities of CPV+RPV

data_CINV$Technology <- ifelse(data_CINV$Technology == "CPV"|data_CINV$Technology == "RPV", "CPV", data_CINV$Technology)
data_CINV <- data_CINV %>% group_by(Technology,Region) %>% summarise(across(everything(), sum))

#progress ratio
data_CINV$PR <- rep(0,nrow(data_CINV)) 
data_CINV$PR <- ifelse(data_CINV$Technology == "CSP", 0.1,
                      ifelse(data_CINV$Technology == "WNO", 0.15,
                             ifelse(data_CINV$Technology == "WND", 0.05,
                                    ifelse(data_CINV$Technology == "CPV",0.2,
                                           ifelse(data_CINV$Technology == "RPV",0.2,0)))))

#Since RPV and CPV scale together for installed cap, just copy the rows to get rooftop
data_CINV <- data_CINV %>% filter(Technology == "CPV") %>% mutate(Technology = "RPV") %>% rbind(data_CINV)
```
Data processing: applying step 1 & step 2 for WND, CPV and RPV

```{r}
source("CINV_fct.R")

data_CINV_WND <- CINV_paste(data_CINV,"WND",costs_WND) %>% CINV_Compute("WND",costs_WND_base)
data_CINV_CPV <- CINV_paste(data_CINV,"CPV",costs_CPV) %>% CINV_Compute("CPV",costs_CPV_base)
data_CINV_RPV <- CINV_paste(data_CINV,"RPV",costs_RPV) %>% CINV_Compute("RPV",costs_RPV_base)
```
For CSP and WNO, starting with IRENA (2020b) regional data and applying the world mean cost reduction.

It is even a cost increase for CSP since new installations come with storage facilities.
```{r}
data_CINV_CSP <- CINV_paste(data_CINV,"CSP",costs_CSP)
data_CINV_WNO <- CINV_paste(data_CINV,"WNO",costs_WNO)

#Source: IRENA (2020) Renewable Power Generation Cost
mean_cost_dec <- list()
mean_cost_dec["CSP"] <- max(0,1 - 5774/5510) #Figt 8.1
mean_cost_dec["WNO"] <- max(0, 1- 3800/5260) #Fig 4.1

data_CINV_CSP <- data_CINV_CSP %>% mutate(CINV_base = CINV_2019/(1-mean_cost_dec[["CSP"]]))
data_CINV_WNO <- data_CINV_WNO %>% mutate(CINV_base = CINV_2019/(1-mean_cost_dec[["WNO"]]))
```

## Final dataset
```{r}
data_CINV_final <- rbind(data_CINV_WND,
                         data_CINV_WNO,
                         data_CINV_CSP,
                         data_CINV_CPV,
                         data_CINV_RPV) %>% select(Technology,Region,CINV_base)
data_CINV_final$CINV_base <- round(data_CINV_final$CINV_base,0)
data_CINV_final$Region <- factor(data_CINV_final$Region, levels = Reg_IMC)

#reorder factors in case of a full csv output. Rename factors WND, WNO etc  
data_CINV_final$Technology <- factor(data_CINV_final$Technology , levels = c("WND","WNO","CSP","CPV","RPV"))
data_CINV_final <- arrange(data_CINV_final, Technology, Region)
```

